Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Refer to figure 2 and revise computer used for analysis

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Air (M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

None of the factors that were tested for had an effect on the reproducibility score.

Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` scored '100' or fully reproducible.

>>>>

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

None of the factors that were tested for had an effect on the reproducibility score.
Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100' or fully reproducible (Figure \@ref(fig:reproScore)).
